### 2018-10-26 paper/complexity.tex
update

>>>>

Let us now  compare test executions of $(Z(\ol s)\parallel[\Sigma] {\ol U}_F(j))$ for
various values of $j$, where ${\ol U}_F(j)$ denotes a failures test case derived from 
reference process $Z(\ol s)$, to executions of $(Z\parallel[\Sigma] U_F(j))$, where
$U_F(j)$ has been derived from $Z$.
\begin{enumerate}
\item For $j<\#\ol s$, $(Z(\ol s)\parallel[\Sigma] {\ol U}_F(j))$ has the same executions 
as $(Z\parallel[\Sigma] U_F(j))$.

\item For $j = \#\ol s$, $(Z(\ol s)\parallel[\Sigma] {\ol U}_F(j))$ has $\card{\minhits(Z/\ol s)}$ fewer executions than $(Z(\ol s)\parallel[\Sigma] U_F(j))$, because 
$Z(\ol s,\ol s)$ has an empty set of hitting sets. As a consequence, test case
${\ol U}_F(\#\ol s)$ cannot enter branch  
\end{enumerate}
